Toward dynamic models of combat or lack thereof in animal mating

### 2016-02-07 ms.tex
comparison between energy budgets and cost functions

\begin{figure}[h!]
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_pc_plot.pdf}
    \caption{Percent energy expenditure of cohort at generation 499}
    \label{fig:energy pc}

    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_total_plot.pdf}
    \caption{Total energy expenditure of cohort at generation 499}
    \label{fig:energy total}
\end{figure}
As patch area increases the number of fight importunities decreases, 
This can probably explain the strong decrease in energy spent fighting. but I have no idea, early days yet.

@@

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_pc_plot.pdf}
    \caption{Flat costs. Percent energy expenditure of cohort at generation 499}
    \label{fig:energy pc}

    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_total_plot.pdf}
    \caption{ Flat costs Total energy expenditure of cohort at generation 499}
    \label{fig:energy total}
\end{figure}
As patch area increases the number of fight importunities decreases,
This can probably explain the strong decrease in energy spent fighting.but I have no idea, early days yet.
\clearpage

\begin{figure}[h!]
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_pc_plot_var.pdf}
    \caption{Variable costs. Percent energy expenditure of cohort at generation 499}
    \label{fig:var energy pc}
    \centering
    \includegraphics[width=8cm,height=10cm,keepaspectratio]{figures/energy_total_plot_var.pdf}
    \caption{Variable costs, Total energy expenditure of cohort at generation 499}
    \label{fig:var energy total}
\end{figure}

The results for variable costs are different, why? from here on all graphs are from the flat cost data...

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/k_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $k$ at max energy}
    \label{fig:k history}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/e_0_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $e_0$  k at max energy}
    \label{fig:e_0 history}
\end{figure}
